### 2017-12-20 writing/paper/sections/wilf.tex
Final fix for DMTCS

If there is an occurrence of \(m_1\) there must be a lowest occurrence of
\(m_1\), \ie, the occurrence has the lowest possible values for any occurrence.
Now consider the top regions, labelled \(A \et B\), the subpermutation contained
in the union of these regions must avoid the permutation \(231\). Also, the
subpermutation in the region \(A\) must be a decreasing subsequence, otherwise
an occurrence of \(231\) will be created with either of the points in the
occurrence of \(m_1\). Now, consider the region labelled \(C\), since we
specified that we were focused on the lowest possible occurrence of \(m_1\) this
region cannot contain an occurrence of either \(m_1\) or \(231\). This is a full
structural decomposition of a container of \(m_1\) inside \(\av{231}\).

>>>>

If there is an occurrence of \(m_1\) there must be an occurrence of \(m_1\) that minimizes
the values of the points \(xy\) in the occurrence, first with respect to \(x\) then with respect to \(y\).
Now consider the top regions, labelled \(A \et B\), the subpermutation contained
in the union of these regions must avoid the permutation \(231\). Also, the
subpermutation in the region \(A\) must be a decreasing subsequence, otherwise
an occurrence of \(231\) will be created with either of the points in the
occurrence of \(m_1\). Now, consider the region labelled \(C\), since we
specified that we were focused on the lowest possible occurrence of \(m_1\) this
region cannot contain an occurrence of either \(m_1\) or \(231\). This is a full
structural decomposition of a container of \(m_1\) inside \(\av{231}\).
